\documentclass{resume}
\input{glyphtounicode}

\pdfgentounicode=1

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry}
\usepackage[colorlinks=true, linkcolor=black, urlcolor=black]{hyperref}

\name{Arun Ranganathan}
\address{\href{mailto:arun.ranga@hotmail.ca}{arun.ranga@hotmail.ca}\ \\
         \href{https://www.linkedin.com/in/arun-ranganathan-860674b1/}{in/arunranganathan} \\
         \href{https://github.com/Arun4rangan}{github.com/Arun4rangan}}

\begin{document}
  \begin{rSection}{Summary}
    \begin{rSummary}
    {
      \item Experience building and maintaining robust distributed scalable systems.
      \item C\texttt{++} (CMake), Python, Java (Android), JavaScript, SQL, Golang, C, NodeJS
      \item Node.js, Django, Angular 2, AngularJS, CloudSQL, PostgreSQL, MySQL, RabbitMQ, Redis, Kubernetes,\\ OpenShift, Celery, gRPC, TensorRT, TensorFlow, OpenVINO, OpenCV, NumPy, Java, Protocol Buffers, React
    }
    \end{rSummary}
  \end{rSection}

  \begin{rSection}{Experience}
    \begin{rSubsection}{Top Hat}{September 2020 – Present}{Full Stack Engineer}{Toronto, ON}
      \item Worked on textbook version control system which accounted for 50\% of Top Hat's revenue.
      \item Developed front end UI for merge control that allows existing content to be updated with professors discretion. 
      \item Improved merge control flow architecture that allows auto-revision of textbooks to be sent between any content.
      \item Refactored old code into more readable code while improving the performance by nearly 90\%.
      \item Formulated a new business idea, created a proposal and worked POC by recruiting 3 software developers and a product manager.
      \item Interviewed software engineering candidates and helped hire few engineers.
      \item Helped debug P0 bugs and device an immediate and long term solution to the problem.
      \item Onboard and mentor new team members and be always be available to pair on a problem. 
    \end{rSubsection}
    \begin{rSubsection}{Paravision}{April 2019 – Present}{Computer Vision Engineer}{Toronto, ON}
    \item Decreased latency by 19\% (P95) and improved throughput by 150\% (P95) by re-architecting streaming app with asynchronous networking and parallel computing principles.
    \item Quadrupled ETL throughput (2MM to 8MM) by scaling with Kubernetes speeding up model training time.
    \item Configure Openshift platform to host micro-services on bare-metal.
    \item Constructed facial recognition gRPC server with clients in C\texttt{\#}, NodeJS, Python3 and C\texttt{++}.
    \item Built liveness C\texttt{++} SDK on Windows and Linux using OpenCV, Tensorflow, TensorRT and OpenVINO.
    \end{rSubsection}
    \begin{rSubsection}{The League}{May 2018 – August 2018}{Backend Developer}{San Francisco, CA}
    \item Develop core micro-services that replaced parts of monolithic backend deployed in GCP Kubernetes.
    \item Reduce number of calls to PostgreSQL by implementing trigger based caching.
    \end{rSubsection}
    \begin{rSubsection}{The League}{January 2018 – April 2018 }{Android Engineer}{San Francisco, CA}
    \item Rewrite the messaging platform. Optimize how messages are received, stored and managed.
    \item Increase user activity by developing custom photo-messaging capabilities in chats and optimizing the loading and uploading of photo-messages.
    \end{rSubsection}
    \begin{rSubsection}{Aspire Financial Technologies}{Augest 2016 – April 2017}{Backend Developer}{Toronto, ON}
    \item Develop query-able RESTful API endpoints on Django.
    \item Engineer aggregating algorithms that compile into complex financial math on PostgreSQL and optimized it to run in real time.
    \end{rSubsection}
  \end{rSection}

  \begin{rSection}{Open Source / Projects}
    \begin{rProjectSection}{\href{https://chrome.google.com/webstore/detail/lavoro/apkdfigakniknjehnfaoopfhihahhnpp?hl=en&authuser=0}{\textbf{Lavoro}}}{ATS Helper}
      \item Chrome extension to better match your resume with the job description. Ranking algorithum to rank keywords in your resume against job description. Built with Vue.js.
    \end{rProjectSection}
    \begin{rProjectSection}{\href{https://github.com/redis/redis}{\textbf{Redis}}}{In-memory Database}
      \item Show threading configuration in INFO output \href{https://github.com/redis/redis/pull/7446}{ \textbf{\#7446} } \& \href{https://github.com/redis/redis-doc/pull/1353}{\textbf{\#1353}}
    \end{rProjectSection}
    \begin{rProjectSection}{\href{https://github.com/cockroachdb/cockroach}{\textbf {CockroachDB}}}{Distributed SQL Database}
      \item Pow binary operator \href{https://github.com/cockroachdb/cockroach/pull/50143}{[\textbf{\#50143}]}. DB2 formatted timestamps \href{https://github.com/cockroachdb/cockroach/pull/50011}{[\textbf{\#50011}]}. Coerce invalid geography \href{https://github.com/cockroachdb/cockroach/pull/50457}{[\textbf{\#50457}]}
    \end{rProjectSection}
    \begin{rProjectSection}{\href{https://github.com/pinojs/pino}{\textbf{Pino}}}{Low overhead Node.js Logger}
      \item Custom log levels and remove default levels \href{https://github.com/pinojs/pino/pull/515}{ [\textbf{\#515}] }. Change log level name \href{https://github.com/pinojs/pino/pull/503}{ [\textbf{\#503}] }
    \end{rProjectSection}
    \begin{rProjectSection}{\href{https://chrome.google.com/webstore/detail/gtasker-extension/lljekoepijafpdebkahcjdhbjaappami?hl=en-GB}{\textbf{gTasker}}}{Chrome Extension}
      \item Create chrome extension to manage day to day tasks while browsing the internet. Performs CRUD operations on Google Oauth2 API and Google Calendar API. This Chrome Extension is published in Google Play Store.
    \end{rProjectSection}
    \begin{rProjectSection}{\href{https://github.com/Arun4rangan/GenoDonor}{\textbf{GenoDonor}}}{Genome encoding hackathon}
      \item Worked with 3 other co-workers to create a front-end using React and Node.JS based backend. Create a Web App for sperm donors where users can filter and search for specific genome traits based on donor.
    \end{rProjectSection}
  \end{rSection}
  

  \begin{rSection}{Education}
    {\bf University of Waterloo} \hfill {\em April 2019} \\ 
    { Bachelor of Applied Science in Honours Nanotechnology Engineering With Distinction }
  \end{rSection}

\end{document}
